Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2023-10-03 RegReport/paper.tex
changed Anna's affiliation

\author{Alasdair D. F. Clarke$^{1}$, Kyle Sauerberger$^{2}$, Anna Nowakowska$^{3}$,\\ David A. Rosenbaum$^{2}$, Thomas R. Zentall$^{4}$ \& Amelia R. Hunt$^{3}$}

\address{$^{1}$Dept. of Psychology, University of Essex, UK\\
$^{2}$Dept. of Psychology, University of California, USA\\
$^{3}$School of Psychology, University of Aberdeen, UK\\
$^{4}$Dept. of Psychology, University of Kentucky, USA}

%%%% Subject entries to be placed here %%%%
\subject{Psychology}

>>>>

\author{Alasdair D. F. Clarke$^{1}$, Kyle Sauerberger$^{2}$, Anna Nowakowska$^{3}$,\\ David A. Rosenbaum$^{2}$, Thomas R. Zentall$^{4}$ \& Amelia R. Hunt$^{5}$}

\address{$^{1}$Dept. of Psychology, University of Essex, UK\\
$^{2}$Dept. of Psychology, University of California, USA\\
$^{3}$School of Psychology and Vision Sciences, University of Leicester, UK\\
$^{4}$Dept. of Psychology, University of Kentucky, USA}
$^{5}$School of Psychology, University of Aberdeen, UK\\
%%%% Subject entries to be placed here %%%%
\subject{Psychology}
